The paper on \Large \bf Blockchain Frontrunning

### 2018-08-30 frontrunning/Latex/sections/paper.tex
[frontrunning] notes from the meeting

\section{Introduction}
% Why is this important.
% PAPER BEING SOLD HERE
%______________________________________________________________%

@@

\subsection{How are Blockchain Applications Vulnerable to Front-running?}
\label{sec:Front Running on the Blockchains}

@@

\subsection{Literature on Tranditional Front-running}
As traditional frontrunning has been the subject of discussion for decades, there are many literatures on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

\subsection{Historical evidence in the Blockchain}
As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection. For examples here we research some of the events of such attacks happening in the Ethereum blockchain applications.

@@

%NOTE: @mahsa: is this considered a Historical evidence? should we talk about this somewhere else and maybe do a PoC on Ghazal for this section?
\subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about front-running in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)
\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets. Front-running can occur within other (non-financial) blockchain applications such as naming systems. Blockchain-based domain registrar have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduce single point of failures in the entire web. One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}. Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names. In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees. This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price. Note that, domain name front-running also occurs in the vanilla system. In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.
% PoC of front-running ghazal
%TODO: also talk about ENS

@@

\subsubsection{Design Decision \#1: Commitment Scheme\newline}
Commitment scheme, also known as \textit{commit and reveal}, is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}. Commitment scheme is a robust method to prevent information leakage from the sensitive transactions. This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash, see Figure~\ref{fig:commitReveal}. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. Depending on the Dapp design, either the order is collateralized, which means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be considered as a DoS attack. 
Another use of such commitment scheme, is in decentralized naming systems, such as Ghazal or ENS. In this case, a user would send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user would send a reveal transaction revealing the bid and also the details of the requested domain. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running. Similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however their participation and weight of the vote are publicly known. 
Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design.

@@

@@

\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed. For example when designing a decentral exchange, one can use \emph{the call market design} instead of a time-sensitive order book. In a call market design, the arrival time of the orders do not matter as they are executed in batches.

>>>>

\section{Introduction}

Have a small discussion about arbitrage and censorship just to show that they orbit around front-running.
For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.

% Why is this important.
% PAPER BEING SOLD HERE
%______________________________________________________________%

@@

\subsection{How are Blockchain Applications Vulnerable to Front-running?} %which blockchain applications?
\label{sec:Front Running on the Blockchains}t

%Jeremy's Comments: Find some examples; you have to justify why you talked about only a specific group of examples. Need to have a criteria for what is vulnerable to frontrunning: like top ten dapps from specific blogs. Have a criteria.

@@

\subsection{Literature on Traditional Front-running}

% talk about the AMF frontrunning.

As traditional frontrunning has been the subject of discussion for decades, there are many literatures on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

\subsection{Historical evidence in the Blockchain}  % JEREMY's COMMENT:  try to sell it in a way that that the audience know that there are 1000 of the applications prone to the frontrunning but we picked 3 because they are different.

As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection. For examples here we research some of the events of such attacks happening in the Ethereum blockchain applications.

@@

%NOTE: @mahsa: is this considered a Historical evidence? should we talk about this somewhere else and maybe do a PoC on Ghazal for this section?
\subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about front-running in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)

%Jeremy's Comment: contrast ghazal vs ens, or try to have some historical evidence for namespace on the Ethereums. Try too make ghazal less central.
%Jeremy's comments: also talk about the "private information retrieval" (Ian Goldberg's work at waterloo)

\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets. Front-running can occur within other (non-financial) blockchain applications such as naming systems. Blockchain-based domain registrar have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduce single point of failures in the entire web. One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}. Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names. In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees. This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price. Note that, domain name front-running also occurs in the vanilla system. In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.
% PoC of front-running ghazal
%TODO: also talk about ENS

@@

\subsubsection{Design Decision \#1: Commitment Scheme\newline} %talk about the drawbacks of this scheme: eg: you may forget to reveal. 
Commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}. Commitment scheme is a robust method to prevent information leakage from the sensitive transactions. This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash, see Figure~\ref{fig:commitReveal}. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. Depending on the Dapp design, either the order is collateralized, which means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be considered as a DoS attack. 
Another use of such commitment scheme, is in decentralized naming systems, such as Ghazal or ENS. In this case, a user would send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user would send a reveal transaction revealing the bid and also the details of the requested domain. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running. Similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however their participation and weight of the vote are publicly known. 
Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design.

@@

\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed to not rely on the time for the orders to be executed. For example when designing a decentral exchange, one can use \emph{the call market design} instead of a time-sensitive order book. In a call market design, the arrival time of the orders do not matter as they are executed in batches [cite Jeremy's prediction markets paper].

@@
